TBD

### 2021-03-17 outputs/paper/paper.Rmd
regressions fixed for S9
tables still need to be cleaned but models are all complete. :)

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"),
          column.labels = c("No Money", "Money"))

@@

# UK, Poland, and US
s9_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40)
s9_main_result <- lm(response ~ cond, data = s9_main)

# UK
s9_uk <- s9_main %>%
  filter(country == 39)
s9_uk_result <- lm(response ~ cond, data = s9_uk)

@@

s9_poland_result <- lm(response ~ cond, data = s9_poland)

# USA
s9_usa <- s9_main %>%
  filter(country == 40)
s9_usa_result <- lm(response ~ cond, data = s9_usa)

# final table
stargazer(s9_main_result, s9_uk_result, s9_poland_result, s9_usa_result, 
          title = "Reporting rates in NoMoney, Money, and Big Money condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```

@@

# final table
stargazer(s10_main_result, s10_uk_result, s10_poland_result, s10_usa_result, 
          title = "Reporting rates in Money-No Key condition", 
          align = TRUE, 
          type = 'latex', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money-NoKey", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```
# Discussion

>>>>

# final table (S8)
stargazer(s8_main_result, s8_money_result, 
          title = "Reporting rates in the Money and No Money Condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Male", "Above 40", "Computer", "Coworkers", "Other Bystanders", "Constant"),
          column.labels = c("No Money", "Money"))

@@

# UK, Poland, and US
s9_main <- dfBehavModel %>%
  filter(country == 39 | country == 27 | country == 40) %>%
  mutate(money = if_else(cond == 1, 1, 0)) %>%
  mutate(big_money = if_else(cond == 2, 1, 0))

s9_main_result <- lm(response ~ money + big_money, data = s9_main)

# UK
s9_uk <- s9_main %>%
  filter(country == 39)
s9_uk_result <- lm(response ~ money + big_money, data = s9_uk)

@@

s9_poland_result <- lm(response ~ money + big_money, data = s9_poland)

# USA
s9_usa <- s9_main %>%
  filter(country == 40)
s9_usa_result <- lm(response ~ money + big_money, data = s9_usa)

# final table
stargazer(s9_main_result, s9_uk_result, s9_poland_result, s9_usa_result, 
          title = "Reporting rates in NoMoney, Money, and Big Money condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money", "Big Money", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```

@@

# final table
stargazer(s10_main_result, s10_uk_result, s10_poland_result, s10_usa_result, 
          title = "Reporting rates in Money-No Key condition", 
          align = TRUE, 
          type = 'text', 
          dep.var.labels = "Response", 
          covariate.labels = c("Money-NoKey", "Constant"),
          column.labels = c("UK, Poland, and US", "United Kingdom", "Poland", "United States"))
```
# Discussion
